\documentclass{beamer}
\input{../../packages.tex}
\input{../../slides_formatting.tex}

%Information to be included in the title page:
\title{Stencil Notes}
\author{Russell Bentley}
\institute{Stony Brook}
\date{2024}

\begin{document}

\frame{\titlepage}

\section{LBM}
\begin{frame}{Nicolas Maquignon}
  \begin{outline}
    \1 Found through guest article on 
    \href{https://feaforall.com/implementation-lattice-boltzmann-method-lbm/}{FEA for all}

    \1 Published several articles about LBM \cite{Maquignon2014}, \cite{Maquignon2022}

    \2 \cite{Maquignon2014} extends model from another paper I can't find.
      
    \2 Condensation models seems like a good periodic problem.

    \1 Was on this article, which seems to have a good overview of LBM and related articles. 
    About splitting problem across GPUs.
    Has references about data access patterns on GPU
    \cite{Duchateau2015}
  \end{outline}
\end{frame}

\begin{frame}
  \begin{outline}
    \1 Attention, intention, and will in quantum physics \cite{Stapp1999}
  \end{outline}
\end{frame}

\begin{frame}{other stencil work}
  \begin{outline}
    \1 Tubostencil, a-periodic that trades space for runtime \cite{Liu2023turbo}
    \2 walBERlA, framwork for HPC block structured problems \cite{Bauer2021}
  \end{outline}
\end{frame}

\begin{frame}{LBM Theory}
  \begin{outline}
    \1 Cumulant paper, Hennig also cited for chimara transforms \cite{Geier2015}
  \end{outline}
\end{frame}

\begin{frame}{LBM Code Generation}
  \begin{outline}
    \1 New Code gen paper with lots of good stuff, \cite{Suffa2024}
    \1 Pystencil paper \cite{Bauer2019}
    \1 Kernkraft paper \cite{Hammer2017}
  \end{outline}
\end{frame}

\begin{frame}{Voronoi Mesh Stuff}
  \begin{outline}
    \1 \cite{Gaburro2021High} Young researchers paper on Higher order ale schemes and space-time slivers, considers how the mesh changes over time, very cool. Seems real paper is:

    \1 \cite{Gaburro2020High} Has springel on it! This one has all the math in it. Not in 3D yet though, 2D only. Plan to integrate with AREPO soon.

    \2 Point to \cite{Re2017Interpolation} for next steps on 3D

    \2 They are excited to try and model the hyperbolic formulation of continuum mechanics in \cite{Dumbser2016High}, and older paper on hyperbolic conservation laws \cite{Dumbser2011Universal}. And another hyperbolic model on viscous newtonian flows \cite{Peshkov2016Hyperbolic}.

    \2 \cite{Guermond2018Second} something about domain presercation in hyperbolic systems?

  \1 \cite{Gaburro2021Well} Gaburro presents a hyperbolic formulation and solver for general relativirty field equations, pretty cool

  \1 \cite{Dumbser2018Conformal} introduces FO-CCZ4 formulation of the einstein equations and presents an implementation. Hyperbolic!

    
  \end{outline}
\end{frame}

\begin{frame}{Vor Mesh More}
\begin{outline}
  \1 Great reference on ENO / WENO schemes \cite{zhang2016eno}
  \1 Original Arepo paper \cite{Springel2010Pur}
  \1 That didn't include MHD, that was added in \cite{pakmor2011mhd}
  \1 Dumbser 2008 paper with their ADER scheme \cite{dumbser2008unified} on unstructured meshes
  \1 Higher order finite volume framework in fortran \cite{antoniadis2022ucns3d}
  \1 \textsc{Gadget-4} paper \cite{springel2021simulating}, focus on scalability and mixed parallelism models. OOh and integer coords, eh mixed parallelism wasn't what I was expecting, openmp not a good fit, yadda yadda. BUT use of RMA and such IS interesting.
\end{outline}
\end{frame}

\begin{frame}[allowframebreaks]{References}
    \tiny
    \printbibliography
\end{frame}


\end{document}

